Direct observation of \swave scattering of fermions crossing a Feshbach resonance

### 2015-02-16 draft1.tex
Added a new first figure to explain absorption imaging

\begin{document}
\newcommand{\swave}[0]{$\it{s}$-wave }
\newcommand{\K}{ $^{40}\rm{K}$}

@@

>>>>

\begin{document}
\newcommand{\swave}[0]{$\it{s}$-wave }
\newcommand{\pwave}[0]{$\it{p}$-wave }
\newcommand{\K}{ $^{40}\rm{K}$}

@@

	\subfigure[]{\includegraphics*[scale=0.6]{Picture1a}}
	\subfigure[]{\includegraphics*[scale=0.6]{Picture1b}}
	\subfigure[]{\includegraphics*[scale=0.4]{Picture1c}}
\caption{Absorption imaging. a. First, a near resonant probe light is shined on the atoms, and the shadow of that light is imaged on the camera. Then, the atoms are allowed to escape their trap and and image of just the probe light is taken. b. An atomic cloud illuminated by a probe light field absorbs photons from the probe and re-emits them in arbitrary directions. This process results in a net velocity of the cloud in the direction of the probe light as well as diffusive spreading in the transverse directions. c. As the probe beam, travels through the atomic cloud, some of its power is absorbed, and the intensity seen by atoms further along the imaging direction $z$ is lowered.  }  
\label{fig:absorptionIntor}
